---
output: github_document
---

```{r setup, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```
# wdm

[![Travis build status](https://travis-ci.org/tnagler/wdm-r.svg?branch=master)](https://travis-ci.org/tnagler/wdm-r)
[![AppVeyor build status](https://ci.appveyor.com/api/projects/status/github/tnagler/wdm-r?branch=master&svg=true)](https://ci.appveyor.com/project/tnagler/wdm-r)

R interface to the [wdm](https://github.com/tnagler/wdm) C++ library, which
provides efficient implementations of weighted dependence measures and related 
independence tests:

   * Pearsons's rho
   * Spearmans's rho
   * Kendall's tau
   * Blomqvist's beta
   * Hoeffding's D
 
All measures are computed in *O(n* log *n)* time, where *n* is the number of 
observations.


## Installation

You can install the development version from [GitHub](https://github.com/) with:

``` r
# install.packages("devtools")
devtools::install_github("tnagler/wdm-r")
```
## Examples

```{r}
library(wdm)
```

####  dependence between two vectors
``` {r}
x <- rnorm(100)
y <- rpois(100, 1)  # all but Hoeffding's D can handle ties
w <- runif(100)
wdm(x, y, method = "kendall")               # unweighted
wdm(x, y, method = "kendall", weights = w)  # weighted
```

####  dependence in a matrix
``` {r}
x <- matrix(rnorm(100 * 3), 100, 3)
wdm(x, method = "spearman")               # unweighted
wdm(x, method = "spearman", weights = w)  # weighted
```

#### independence tests
``` {r}
x <- rnorm(100)
y <- rpois(100, 1)  # all but Hoeffding's D can handle ties
w <- runif(100)
indep_test(x, y, method = "kendall")               # unweighted
indep_test(x, y, method = "kendall", weights = w)  # weighted
```

