---
output: github_document
---

```{r setup, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```
# wdm

[![R-CMD-check](https://github.com/tnagler/wdm-r/actions/workflows/R-CMD-check.yaml/badge.svg)](https://github.com/tnagler/wdm-r/actions/workflows/R-CMD-check.yaml)
[![CRAN status](https://www.r-pkg.org/badges/version/wdm)](https://cran.r-project.org/package=wdm)
![CRAN downloads](http://cranlogs.r-pkg.org/badges/wdm)

R interface to the [wdm](https://github.com/tnagler/wdm) C++ library, which
provides efficient implementations of weighted dependence measures and related 
independence tests:

   * Pearsons's rho
   * Spearmans's rho
   * Kendall's tau
   * Blomqvist's beta
   * Hoeffding's D
 
All measures are computed in *O(n* log *n)* time, where *n* is the number of 
observations. 

For a detailed description of the functionality, see the 
[API documentation](https://tnagler.github.io/wdm-r/).


### Installation

- the stable release from CRAN:

``` r
install.packages("wdm")
```

- the development version from [GitHub](https://github.com/) with:

``` r
# install.packages("devtools")
install_submodule_git <- function(x, ...) {
  install_dir <- tempfile()
  system(paste("git clone --recursive", shQuote(x), shQuote(install_dir)))
  devtools::install(install_dir, ...)
}
install_submodule_git("https://github.com/tnagler/wdm-r")
```

### Cloning

This repo contains [wdm](https://github.com/tnagler/wdm) as a submodule. For 
a full clone use
``` shell
git clone --recurse-submodules <repo-address>
```

### Examples

```{r}
library(wdm)
```

#####  Dependence between two vectors
``` {r}
x <- rnorm(100)
y <- rpois(100, 1)  # all but Hoeffding's D can handle ties
w <- runif(100)
wdm(x, y, method = "kendall")               # unweighted
wdm(x, y, method = "kendall", weights = w)  # weighted
```

#####  Dependence in a matrix
``` {r}
x <- matrix(rnorm(100 * 3), 100, 3)
wdm(x, method = "spearman")               # unweighted
wdm(x, method = "spearman", weights = w)  # weighted
```

##### Independence test
``` {r}
x <- rnorm(100)
y <- rpois(100, 1)  # all but Hoeffding's D can handle ties
w <- runif(100)
indep_test(x, y, method = "kendall")               # unweighted
indep_test(x, y, method = "kendall", weights = w)  # weighted
```

